Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-07-15 draft.tex
remove reduction by mu from list of period actions
revise rest of timeline and following paragraph; remove first paragraph of sec 2.2.1

\begin{enumerate} 
\item The status quo payoffs for $s$ are reduced by $\mu$.

\item $p$ chooses an investment level $R_p^t\in \mathbb{R}^+$.

\item $c$ chooses an investment level $R_c^t\in \mathbb{R}^+$.

\item Conflict Stage Game: $s$ and $g$ play a stage game in which each chooses simultaneously from the following actions: $\{\text{Fight, Status Quo, Cede}\}$. 
\end{enumerate}

The payoffs at the end of a period are determined by these actions and six state variables. These state variables keep track of the value of the status quo ($Q_s^t$ and $Q_g^t$), losing ($L_s^t$ and $L_g^t$) and winning the issue of status ($W_s^t$ and $W_g^t$) for the secessionists and government respectively. These values evolve as the patron and player $c$ make investments and the status quo payoffs degrade over time.

@@

\subsubsection{Within-period Payoffs for the Patron and International Community}

At the start of each period, the patron, $p$, and player $c$ may invest resources to affect the payoffs of $s$ and $g$ in the stage game according to Equation~\ref{eqn:motion} below. $B_p^t$ denotes the total that the patron can devote to interceding in the conflict; we assume that player $c$, which is often a large coalition of states, does not have a binding budget constraint.

We assume player $c$ prefers peace to war. For simplicity, we limit our modeling of $c$'s preference for peace to the assumption that $c$ will not choose to fund a military buildup that it expects will induce war. This assumption is not necessary for the basic results to hold; however, it justifies our decision not to address military support of armed reconquest by the home state as a deliberate strategy by $c$ to achieve reunification.

>>>>

\begin{enumerate} 
\item $p$ chooses an investment level $R_p^t\in \left[0,B_p^t\right]$ to influence the payoffs of $s$ and $g$, where $B_p^t$ is an exogenous limit on the finances of the patron.

\item $c$ chooses an investment level $R_c^t\in \mathbb{R}^+$ to influence the payoffs of $s$ and $g$.\footnote{We assume that player $c$, which is often a large coalition of states, does not have a binding budget constraint.}

\item Conflict Stage Game: $s$ and $g$ play a stage game in which each chooses simultaneously from the following actions: Fight, Status Quo, Cede. 
\end{enumerate}

The payoffs at the end of a period are determined by these actions and six state variables. These state variables keep track of the value of the status quo ($Q_s^t$ and $Q_g^t$), losing ($L_s^t$ and $L_g^t$) and winning the issue of status ($W_s^t$ and $W_g^t$) for the secessionists and government respectively. The transitions of the state variables are described below.

@@

\subsubsection{Within-period Payoffs for the Patron and International Community}
We assume player $c$ prefers peace to war. For simplicity, we limit our modeling of $c$'s preference for peace to the assumption that $c$ will not choose to fund a military buildup that it expects will induce war. This assumption is not necessary for the basic results to hold; however, it justifies our decision not to address military support of armed reconquest by the home state as a deliberate strategy by $c$ to achieve reunification.
